Towards understanding the central limit theorem by learning Python basics

### 2021-03-13 paper/article.tex
Fix minor details
Fix typo

More importantly, we conjecture that making a difference between a discrete distribution and a continuous one may be
a big jump in the level of understanding for the student. Discrete distributions are \textit{never} normal,
and to speak about a Gaussian distribution one should introduce the notion of limit in a very
delicate form. Here, we should translate the random variable $X$ to have the expected value $0$ first,
and then normalize it by a function of $d$. We did not see any sign of this concept among the
students' solutions. Maybe, in a next project, we will explicitly ask the students to try to
\textit{approximate} the discrete distributions with a continuous one, by searching for the adequate
expected value and standard deviation. Also, experimenting with higher values for $d$ should also be
suggested---no student
tried to increase the value of \texttt{max\_dice}, even if technically it is possible to try
\texttt{max\_dice = 8} in a \texttt{cocalc.com} Sage session. (Fig.~\ref{10} shows the output
for \texttt{max\_dice = 10} when run natively on a recent computer, after about 1 minutes
of computation. Here we warn the reader that a sample space $\Omega$ with more than 60 millions of elements
must be observed, since $|\Omega|=6^{10}=60,466,176$.)

@@

We are thankful to our students Alexander, Romana, Sandra and Sarah
for their participation in the project.

>>>>

More importantly, we conjecture that making a difference between a discrete distribution and a continuous one may be
a big jump in the level of understanding for the student. Discrete distributions are \textit{never} normal,
and to speak about a Gaussian distribution one should introduce the notion of limit in a very
delicate form. Here, we should translate the random variable $X$ to have the expected value $0$ first,
and then normalize it by a function of $d$. We did not see any sign of this concept among the
students' solutions. Maybe, in a next project, we will explicitly ask the students to try to
\textit{approximate} the discrete distributions with a continuous one, by searching for the adequate
expected value and standard deviation. Also, experimenting with higher values for $d$ should also be
suggested---no student
tried to increase the value of \texttt{max\_dice}, even if technically it is possible to try
\texttt{max\_dice = 8} in a \texttt{cocalc.com} Sage session. (Fig.~\ref{10} shows the output
for \texttt{max\_dice = 10} when run natively on a recent computer, after about 1 minute
of computation. Here we warn the reader that a sample space $\Omega$ with more than 60 millions of elements
must be observed, since $|\Omega|=6^{10}=60,466,176$.)

@@

We are thankful to the students Alexander, Romana, Sandra and Sarah
for their participation in the project.
